Contracts for Contracts

### 2022-12-13 paper.tex
related work

For example, Solidity provides first-order assertion primitives @require@ and
@assert@, but they cannot check function values (e.g. used as callbacks), which are a
common pattern used in smart contract programs. Attackers are able to utilize
the callback mechanism to \note{do crazy things and steal money}

@@

\paragraph{\textbf{Behavioral Contracts for Smart Contracts}}
Behavioral contracts provide a mechanism for programmers to specify assumptions
and guarantees of software components. The specified assumptions and guarantees
will be monitored and reported when violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
Design-by-Contract methodology \cite{DBLP:conf/tools/Meyer98a}, behavioral
contracts have been widely adopted in Java, Haskell, C\#, Python, Racket, etc. \todo{cite}

@@

@@

\subsubsection*{Contributions} This paper makes the following contributions:
\begin{itemize}
  \item We propose to add temporal and higher-order contracts to smart contract
    languages to improve the safety and reliability. We use Solidity to
    demonstrate our proposal.
  \item We present the core language ``Contract Solidity'' with our
    proposed extension, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world cases and show that our proposal is
    effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal.
\end{itemize}

@@

@@

the implementation that modidifies the off-the-shelf Solidity compiler that
supports contracts and generates code with correct contracts checking

@@

>>>>

For example, Solidity provides first-order assertion primitives @require@ and
@assert@, but they cannot check function values (e.g. used as callbacks), which are a
common pattern used in smart contract programs. Attackers are able to utilize
the callback mechanism to \note{do crazy things and steal money}
Solidity also provides the @modifier@ mechanism that intercepts
before and after a function call, thus can be used to check
pre- and post-conditions.
\todo{can we compose modifier?}
\todo{can we attach modifier to callbacks?}
\todo{can we use modifier to check function's argument?}

@@

\subsubsection*{\textbf{Behavioral Contracts for Smart Contracts}}
Behavioral contracts provide a mechanism for programmers to specify assumptions
and guarantees of software components. The specified assumptions and guarantees
will be monitored and reported when violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
Design-by-Contract methodology \cite{DBLP:conf/tools/Meyer98a}, behavioral
contracts have been widely adopted in Java, Haskell, C\#, Python, Racket, etc. \todo{cite}

@@

At the conceptual level, behavioral contracts is complementary to smart
contracts, in this sense that they are both agreement -- between software
components for the former, and between transactional parties for the later.
Thus, the two ``contracts'' indeed mean the same thing but just different levels
of enforcement.

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We propose to add temporal and higher-order contracts to smart contract
    languages to improve the safety and reliability. We use Solidity to
    demonstrate our proposal.
  \item We present the core language ``Contract Solidity'' with our
    proposed extension, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world cases and show that our proposal is
    effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal.
\end{itemize}

@@

\subsection{Comparison with \texttt{modifier}}

@@

the implementation that modifies the off-the-shelf Solidity compiler that
supports contracts and generates code with correct contracts checking

@@

\subsubsection*{\textbf{Behavioral Contracts}}

temporal higher-order contract \cite{DBLP:conf/icfp/DisneyFM11}

\subsubsection*{\textbf{Smart Contracts}}

runtime validation, reduce overhead of runtime checks \cite{DBLP:conf/pldi/LiCL20}

security analyzer \cite{DBLP:conf/pldi/BrentGLSS20}

nondeterminisitic payment bugs \cite{DBLP:journals/pacmpl/WangZS19}

behavioral simulation to verify smart contracts \cite{DBLP:conf/pldi/BeillahiCEE20}

formal and modular specification of smart contracts \cite{DBLP:journals/pacmpl/BramEMSS21}

static analysis to infer ownership and commutativity summaries, for parallelism
\cite{DBLP:conf/pldi/Pirlea0S21}

callbacks \cite{DBLP:journals/pacmpl/AlbertGRRRS20, DBLP:journals/pacmpl/GrossmanAGMRSZ18}

reduce gas consumption \cite{DBLP:journals/pacmpl/GrechKJBSS18}

static analysis of Ethereum \cite{DBLP:journals/pacmpl/SmaragdakisGLTT21}
